Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2022-02-15 edubots_surveys.Rnw
Eliminates markers

Along this line of research, our previous work \cite{MoraChatbots2021:anon}
aimed at analysing the expectations of students on this regard; recent papers
have also analysed how the use of chatbots affected the learning outcomes of
students in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper
analysed conversational chatbots in an one-to-one setting, finding that learning
really benefited from it. This is, once again, a proof of the benefit of
chatbots in certain settings; however, there are some \textcolor{black}{prior experiences, as well as needs} that might
prevent the successful acceptance of the technology, and these are what we are
trying to find out in this paper, together with what kind of features would \textcolor{black}{improve
its acceptance}.

>>>>

Along this line of research, our previous work \cite{MoraChatbots2021:anon}
aimed at analysing the expectations of students on this regard; recent papers
have also analysed how the use of chatbots affected the learning outcomes of
students in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper
analysed conversational chatbots in an one-to-one setting, finding that learning
really benefited from it. This is, once again, a proof of the benefit of
chatbots in certain settings; however, there are some prior experiences, as well as needs, that might
prevent the successful acceptance of the technology, and these are what we are
trying to find out in this paper, together with what kind of features would improve
its acceptance.
